When Subgraph Isomorphism is Really Hard, and Why This Matters for Graph Databases

### 2018-02-14 paper/paper.tex
Poor (review 2)

In \cref{section:filterverify} we look at some of the datasets commonly used to test graph database
systems, which the literature suggests are hard to solve. Simple experiments show that the entire
perceived difficulty of each of these datasets comes down to the widespread use of especially poor
subgraph isomorphism algorithms. Our fourth contribution is to show that the simplest constraint
programming approach, even without the more sophisticated recent advances in subgraph algorithms,
makes the entire graph database filter~/ verify paradigm unnecessary.  Finally, we explain why
filter~/ verify and other recently proposed techniques cannot be beneficial even on more challenging
instances, unless the chosen subgraph isomorphism algorithm exhibits unnecessarily poor behavior
on certain classes of instance.

@@

However, by far the biggest problem is in graph databases. The following section shows how
widespread use of poor subgraph isomorphism algorithms has not just led to overly pessimistic
conclusions regarding performance, but has misdirected the design of larger systems.

>>>>

In \cref{section:filterverify} we look at some of the datasets commonly used to test graph database
systems, which the literature suggests are hard to solve. Simple experiments show that the entire
perceived difficulty of each of these datasets comes down to the widespread use of particular
subgraph isomorphism algorithms, rather than inherent hardness. Our fourth contribution is to show
that the simplest constraint programming approach, even without the more sophisticated recent
advances in subgraph algorithms, makes the entire graph database filter~/ verify paradigm
unnecessary.  Finally, we explain why filter~/ verify and other recently proposed techniques cannot
be beneficial even on more challenging instances, unless the chosen subgraph isomorphism algorithm
exhibits unnecessarily poor behavior on certain classes of instance.

@@

However, by far the biggest problem is in graph databases. The following section shows how
widespread use of weak subgraph isomorphism algorithms has not just led to overly pessimistic
conclusions regarding performance, but has misdirected the design of larger systems.
